
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[letterpaper,left=0.75in,top=1in,right=0.75in,bottom=0.6in]{geometry} % Document margins
%\usepackage[letterpaper,left=0.75in,top=0.7in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{hyperref}
\usepackage{fixltx2e}
\usepackage[misc]{ifsym}
\usepackage{fontawesome}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sangjun Son} % Your name

\address{1, Gwanak-ro, Gwanak-gu, Seoul, Republic of Korea, 08826}
\address{\Letter{} lucetre@snu.ac.kr \space \space \faPhone{} +82 10 3831 0094
\space \space \faGithub{} \href{https://lucetre.github.io/about}{lucetre.github.io}} 
\address{\large\texttt{lucetre}}

\begin{document}
\setlist[itemize,1]{leftmargin=\dimexpr 26pt-2mm}
\setlist[itemize,2]{leftmargin=\dimexpr 26pt-5mm}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{RESEARCH INTERESTS}
%My research interests focuses on tensor analysis/data mining and machine learning.
%\begin{itemize}
%    \item Tensor analysis/Data mining: patterns and models from tensors, and scalable analysis using GPUs
%    \item Machine Learning: Interpretable learning, spatiotemporal learning, time-series, bioinformatics 
%\end{itemize}
%My research interests focuses on {\bf Big Data Mining} and {\bf Interpretable Machine Learning} dealing with data having special structures, such as multi-aspect data, time series, spatiotemporal data, and biological data. 
Machine Learning, Data Mining, Tensor Analysis
\end{rSection}
%
\begin{rSection}{EDUCATION}
{\bf Seoul National University}, \textit{Seoul, Republic of Korea} \hfill Mar. 2016 - Present \\
Candidate for B.S. in Computer Science and Engineering \\
Interdisciplinary Major in Entrepreneurship

{\bf Daegu Science High School}, \textit{Daegu, Republic of Korea} \hfill Mar. 2013 - Feb. 2016
\end{rSection}

%----------------------------------------------------------------------------------------
%	PREPRINTS   SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PUBLICATIONS}
Dawon Ahn, \textbf{Sangjun Son}, and U Kang, \\
	``\href{https://dl.acm.org/doi/abs/10.1145/3340531.3417413}
	{\textbf{Gtensor: Fast and Accurate Tensor Analysis System using GPUs}}," \\
	\textit{29th ACM International Conference on 
	Information and Knowledge Management (CIKM) 2020}, Virtual Event, Ireland
	
\textbf{Sangjun Son}*, Yongchan Park*, Minyong Cho, and U Kang, \\ 
	``\href{https://datalab.snu.ac.kr/dao-cp/}
	{\textbf{DAO-CP: Data-adaptive online CP decomposition}}," 
    \textit{make publicly available}, (* Both authors contributed equally to this work)
\end{rSection}

%--------------------------------------------------------------------------------
%    RESEARCH EXPERIENCES
%--------------------------------------------------------------------------------
\begin{rSection}{RESEARCH EXPERIENCES}
\href{https://datalab.snu.ac.kr/}{\textbf{Data Mining Laboratory}}, \textit{Seoul National University} \hfill Nov. 2019 - Present \\
Research Internship (Advisor: Prof. U Kang)
\vspace{-1mm}
\begin{itemize}
  \item[$\circ$] \textbf{Gtensor}, \textbf{BIGtensor}: Accelerated large-scale tensor analysis on heterogenous system \vspace{-1mm}
  \item[$\circ$] \textbf{DAO-CP}: Enhanced accuracy for CP decomposition of time-evolving tensors by a data-adaptive algorithm
\end{itemize}
\href{https://rubis.snu.ac.kr/}{\textbf{Real-Time Ubiquitous Systems Laboratory}}, \textit{Seoul National University} \hfill Jul. 2017 - Feb. 2018 \\
Research Internship (Advisor: Prof. Chang-Gun Lee)
\vspace{-1mm}
\begin{itemize}
  \item[$\circ$] Implemented simulation to study effects of AED delivery using unmaned vehicle transport technology on defibrillation in out-of-hospital cardiac arrest
\end{itemize}
\end{rSection}

%--------------------------------------------------------------------------------
%    WORKING EXPERIENCES
%--------------------------------------------------------------------------------
\begin{rSection}{WORKING EXPERIENCES}
{\bf Google Software Engineering Intern}, \textit{Google Korea LLC., Desktop Search Team} \hfill Jun. 2021 - Sep. 2021 \\ 
Automatic I2F and Nesting config generation for hOSRP to diOSRP conversion \\
Designed an internal development tool for efficient development in OSRP migration \\
\end{rSection}

%--------------------------------------------------------------------------------
%    TEACHING EXPERIENCES
%--------------------------------------------------------------------------------
\begin{rSection}{TEACHING EXPERIENCES} 
{\bf International Students Integrated Peer Tutoring Program}, \textit{Undergraduate Student Tutor} \hfill Spring. 2021 \\
Data Structures \& Algorithm Fundamentals, \href{https://dorm.snu.ac.kr/}{SNU Gwanak Residence Halls}

{\bf Digital Computer Concept and Practice}, \textit{Lab Class Lecturer} \hfill Fall. 2020 \\
Introduction to Python and Its Application, \href{https://cse.snu.ac.kr/}{Dept. of Computer Science and Engineering}

{\bf Basic Computing: First Adventures in Computing}, \textit{Teaching Assistant} \hfill Fall. 2020 \\
Python Basics, \href{https://liberaledu.snu.ac.kr/}{SNU Faculty of Liberal Education}

{\bf Basic Calculus 1}, \textit{Undergraduate Student Tutor} \hfill Spring. 2020 \\
\href{http://www.math.snu.ac.kr/}{TA Office of the Department of Mathematical Sciences}
\end{rSection}

%--------------------------------------------------------------------------------
%    SOFTWARE
%--------------------------------------------------------------------------------
% \vspace{-1mm}
\newpage
\begin{rSection}{SOFTWARE}
% \vspace{-4mm}
\href{https://datalab.snu.ac.kr/bigtensor/}{\bf BIGtensor},
\textit{Contributor of BIGtensor-GPU and Hadoop} \hfill Nov. 2019 - Feb. 2021 \\ 
Tensor mining packages for large-scale tensor analysis

\href{https://github.com/rubis-lab/DroneTransferSimulator/}{\bf Drone Transfer Simulator}  \hfill Jul. 2017 - Feb. 2018 \\
Simulation of AED drone delivery to defibrillation for patients with out-of-hospital cardiac arrest
\end{rSection}

%----------------------------------------------------------------------------------------
%	COURSE PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{COURSE PROJECTS}
{\bf Deep learning-based wrinkle detection}, \href{https://morpheus3d.co.kr/}{\textit{Morpheus3D}} \hfill Fall. 2020\\
Built new models to segment wrinkle parts in 3D scanned face images by exploiting state-of-art methods 

{\bf ABC}, \textit{Art with Block-Chain: media-art platform} \hfill Spring. 2020\\
Designed a platform where any creator can upload their own media arts and increase profits \\
Implemented smart contract on ERC-721 token, which records its metadata and p5.js-based content on blockchain

{\bf BusyWrite}, \textit{Team writing solution to accelerate collaboration} \hfill Fall. 2017\\
Implemented a concept of a unit of thought that users write on, called \textit{Bubble}, 
and enabled users to write simultaneously and merge after resolving conflicts

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
Programming Languages \ & C++, Python, Java, MATLAB, Scala, Solidity, R (Welcome to any languages) \\
%
Frameworks & PyTorch, Tensorflow, React, AngularJS, Django \\ 
		   & OpenCL, OpenGL, Hadoop, MFC
\end{tabular}
\end{rSection}


\begin{rSection}{HONORS and AWARDS}
{\bf Merit-based Scholarship (full amount)}, \textit{Seoul National University} \hfill Fall. 2020 - Spring. 2021

{\bf SNU Development Fund Scholarship}, \textit{Seoul National University} \hfill Spring. 2017 - Fall. 2017

{\bf Korea Olympiad in Informatics}, \textit{National Programming Contest for High School Students} \hfill May. 2015\\
Silver medal (the 3rd place)

\end{rSection}

%----------------------------------------------------------------------------------------
%	Courses
%----------------------------------------------------------------------------------------

%\begin{rSection}{COURSES COMPLETED}

%{\bf Computer Science} \textit{FIRA} \hfill  2018\\ 
%Introduction to programming, Discrete Math, Database, Advanced Database,
%        			   Data Mining, Deep Learning, Big Data Processing (MongoDB), 
%        			   Distributed System (Spark, Hadoop)
%    \end{itemize}
%    \begin{itemize}
%    \item {\bf Mathematics} \textit{B.S} \vspace{-1mm} \hfill 2014 -2019\\ \vspace{-3mm} 
%    \begin{itemize} \itemsep -4pt \vspace{-1mm} 
%        \item[$\circ$] Linear Algebra, Complex Algebra, Number Theory, Modern Algebra 
%    \end{itemize}
%    \item {\bf Computer Science} \textit{FIRA} \hfill  2018\\ \vspace{-3mm} 
%    \begin{itemize} \itemsep -4pt \vspace{-1mm} 
%        \item[$\circ$] Introduction to programming, Discrete Math, Database, Advanced Database,
%        			   Data Mining, Deep Learning, Big Data Processing (MongoDB), 
%        			   Distributed System (Spark, Hadoop)
%    \end{itemize}
%    \item {\bf Computer Science} \textit{Coursera} \hfill 2020\\ \vspace{-3mm} 
%    \begin{itemize} \itemsep -4pt \vspace{-1mm} 
%        \item[$\circ$] 
%    \end{itemize}
%    \end{itemize}

%\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITIES & HONORS and AWARDS   SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXTRA-CURRICULAR ACTIVITIES}
%

{\bf WD Partners}, \textit{Consulting Firm providing indoor ventilation solution} \hfill Jun. 2021 - Now\\
Theoretically found conditions with the most optimal ventilation efficiency through \\
CFD (Computerized Fluid Dynamics) analysis for pollutants like (e.g., fine dust and droplets containing viruses) \\
Built a prototype device using Coanda effect for real-world validation 

{\bf Problem Solving in SNU}, \textit{Study group for preparing problem-solving interview} \hfill Jun. 2021 - Now \\
Opened weekly practices and workshops to share and learn skills and strategies with each other

{\bf \href{https://decipher.ac/}{Decipher}}, \textit{Blockchain Research Group in Seoul National University} \hfill Mar. 2020 - Aug. 2020\\
Attended weekly seminars about various blockchain topics as a member of StuDeFi \\
Designed a donation platform, AID-U for contributing student education expenses 

{\bf \href{http://paiksbeer.com/}{Paik’s Beer}} \hfill Dec. 2019 - Mar. 2020\\
Served beer and snacks as a part-time job after school \

{\bf \href{https://www.army.mil.kr/}{Republic of Korea Army}}, \textit{Obligatory Military Service} \hfill Feb. 2018 - Oct. 2019 \\
Discharged on full-term military service \\
Occupational specialty: administration, communication equipment operation, chaplaincy 

{\bf \href{http://kasttc.kr/}{KASTTC}}, \textit{Table Tennis Club} \hfill Dec. 2016 - Dec. 2017\\
Conducted lessons to improve the skills of members, managed participating competitions, and supervised weekly training as a club's trainer \

\end{rSection}


%\begin{rSection}{VOLUNTEER EXPERIENCE}
%
%{\bf THE AI KOREA CONFERENCE} \textit{Korean Institute of Information Scientists and Engineers} \hfill Jul. 2019 \\
%Staff as moderating Q$\&$A and alerting the team in case of technical issues
%\end{rSection}


\end{document}
